Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-05 paper_jasa.tex
Mosteller reference to type III error (pdf of paper is on dropbox)

>>>>

\hh{From figure \ref{fig:power_loess3} we see that identification of the data plot is high independently of the effect size. This might be an indication that participants were not considering slope as distinguishing feature for the data, but the apparent clustering, i.e. the null hypothesis is being rejected, but not for the reason of the slope -- which the experimental setup was asking for --  leading to a type III error of `correctly rejecting the null hypothesis for the wrong reason', as defined by \citet{mosteller:48}.}
